Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-08-23 manuscript/manuscript.tex
Minor corrections manuscript

Lithosphere density variation with depth has been studied for almost a century. 
\citet{Athy1930} obtained a decreasing exponential relation between both quantities by studying shale samples.
In the following years, other density functions have been proposed for different rock types \citep[e.g.,][]{Maxant1980, Rao1986, Rao1993, Rao1994}.
Furthermore, the density variation with depth has been taken into account in forward and inversion gravity models, mostly applied to grabens and basins \citep{Cordell1973, Rao1986, Cowie1990, Rao1993, Rao1994, Zhang2001, Welford2010}.

>>>>

Lithosphere's density variation with depth has been studied for almost a century. 
\citet{Athy1930} obtained a decreasing exponential relation between both quantities by studying shale samples.
In the following years other density functions have been proposed for different rock types, such as linear, quadratic and exponential \citep[e.g.,][]{Maxant1980, Rao1986, Rao1993, Rao1994}.
Furthermore, the density variation with depth has been taken into account in forward and inversion gravity models, mostly applied to grabens and basins \citep{Cordell1973, Rao1986, Cowie1990, Rao1993, Rao1994, Zhang2001, Welford2010}.
